Continous time Markov chain models; \\ extension, simulation and visualisation

### 2015-02-11 Response.tex

\end{itemize}

% 2
\item {
{\it
\textbf{
It is sometimes unclear in Chapter 2 whether the analysis is performed under a fixed evolutionary tree or not. 
This is especially so in the evaluation of Bayes Factors in Table 2.3. 
It would also have been nice to understand better whether the use of the epoch model (versus not) has an essential impact on tree reconstruction. 
Somewhat related, it would have been nice to learn from the simulation study how mislead one could be if the data were generated under an epoch model, but analyzed under a simpler model. 
I am not asking for additional analyses here, but merely for additional clarification or insight.
}% END: textbf
}% END: it
}% END: item
\\
% FB: I don't get the first part of this comment. In the Intro we clearly write:
% "Our Bayesian approach also does not condition on a fixed tree topology but averages over all plausible evolutionary histories." (p 46) \\
% PL: OK, but to make it even more explicit I have added this to the results section (in simulation results): 'In all our analyses of the replicate data, as well as in the analyses of the real-world data sets in the next sections, we consider the tree as random and estimate it from the nucleotide data.' (this still needs to be tagged).
To re-iterate the fact that our model does not condition on a known tree topology we now write:

\begin{quote}
\myeditsvtwo
\end{quote}

We now also performed a number of additional simulations in order to explore the impact of correcting for time-heterogeneity on tree reconstruction.
The results of these simulations can serve as a basis for discussion during the thesis defence.
%The simulations which address the second part of this comment are now being performed, I will discuss them during the public defence.

@@

with the assumption of

and which start with:

\begin{quote}
\myeditsvsixone
\end{quote}

In addition to explaining the implications of this assumption from biological perspective, we also briefly introduce some of the recent attempts to relax this assumption, both in the Bayesian phylogeographic framework and more broadly in the context of phylogenetic applications:

### 2015-02-11 chapters/chapter01.tex
more revision editing

\myedit{svsixtwo}{
Realistic substitution processes are however unlikely to be time-reversible, especially since abandoning stationarity and homogeneity assumptions implies abandoning reversibility of the evolutionary process.
Recenty however procedures have also been developed to compute phylogenetic likelihoods under non-reversible models \citep{Boussau2006}, making the use of non-reversible models plausible also for large state-space discrete phytogeographic applications \citep{Edwards2011}.
}

@@

Unlike the molecular data, which is typically dense, the location data is sparse, with only one observation per taxon and many transitions are likely to remain observed.
For this reason, a Bayesian stochastic search variable selection (BSSVS, see also Subsection~\ref{sub:clocks}) procedure has been proposed in order to allow exchange rates in $\mathbf{\Phi}$ that do not contribute to the phytogeographic diffusion to shrink to zero with a certain probability.

>>>>

\myedit{svsixtwo}{
Realistic substitution processes are however unlikely to be time-reversible, especially since abandoning stationarity and homogeneity assumptions implies abandoning reversibility of the evolutionary process.
Recently however procedures have also been developed to compute phylogenetic likelihoods under non-reversible models \citep{Boussau2006}, and such non-reversible models have also been explored for large state-space discrete phylogeographic applications \citep{Edwards2011}.
}

@@

Unlike the molecular data, which is typically dense, the location data is sparse, with only one observation per taxon and many transitions are likely to remain observed.
For this reason, a Bayesian stochastic search variable selection (BSSVS, see also Subsection~\ref{sub:clocks}) procedure has been proposed in order to allow exchange rates in $\mathbf{\Phi}$ that do not contribute to the phylogeographic diffusion to shrink to zero with a certain probability.
